Halving the cost of quantum addition

### 2017-09-12 paper.tex
Changes based on Matt's comments

Our adder uses temporary logical-AND operations, which we draw as wires emerging out of a pair of controls then later merging into an equivalent pair of controls.
\autoref{fig:temporary-logical-AND} shows how we compute the logical-AND of the two controls (which we draw as a wire emerging from two controls then heading rightward), and also the corresponding uncomputation (which we draw as a wire turning upward into two controls).

@@

For over a decade, the T-count of addition has been $8n + O(1)$ \citep{Amy2013, Barenco1995, Cuccaro2004}.
In this paper we showed how to halve the leading factor of this cost by replacing Toffolis in compute/uncompute pairs with temporary logical-ANDs.
The temporary logical-AND is a basic circuit construction widget that can be used in many circuits, and a good example of measurement breaking the symmetry between computation and uncomputation (allowing one to be more efficient than the other).
We covered a few examples of optimizing T-counts with our constructions but, for brevity, we leave further low hanging fruit as an exercise for the reader.

>>>>

Our adder uses temporary logical-AND operations, which we draw as wires emerging out of a pair of controls then later merging into the same pair of controls.
\autoref{fig:temporary-logical-AND} shows how we compute the logical-AND of the two controls (which we draw as a wire emerging from two controls then heading rightward), and also the corresponding uncomputation (which we draw as a wire turning upward into two controls).

@@

For over a decade, the T-count of addition has been $8n + O(1)$ \citep{Amy2013, Barenco1995, Cuccaro2004}.
In this paper we showed how to halve the leading factor of this cost by replacing Toffolis in compute/uncompute pairs with temporary logical-ANDs.
The temporary logical-AND is a basic circuit construction widget that can be used in many circuits, and a good example of measurement breaking the symmetry between computation and uncomputation (allowing one to be more efficient than the other).
We demonstrated how to optimize the T-count of a few tasks using our adder and the temporary logical-AND, but there are many other low hanging applications.
